---
title: "running-chartlbi"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{running-chartlbi}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# 1. Installing `chartlbi` package
For this vigenette to work `chartlbi` must be installed and exist in R's default libpath.

```{r setup}
# devtools::install_github("d2gex/chartlbi")

```

# 2. Reading the sample data
A data sample of a demersal species from the northern waters of the Iberian peninsula has been provided. Although the data has been made up, the details should
be pretty realistic. The timeseries stretches from 2004 to 2016. A sample of the matrix is showed below.
```{r sample_data_reading}
length_freq_matrix <- readRDS("data/demersal_fish_sample.rds")
head(length_freq_matrix)
```

# 3. Running chartlbi
Running `chartlbi` is pretty simple. It only requires 4 parameters:

1. Data results from the LBI algorithm
2. A context shaping the visualisation of the results. You may not need to change the default values to start with.
3. The thresholds against which the results will be evaluated. Default values have been provided, and you will hardly ever need to modify this.
4. The order you would like the indicator to appear following a bottom-top approach.
```{r fig.width=8, fig.height=15}

# (1) Define biological inputs and size of class length
params <- list(
  binwidth = 1,
  linf = 49.1,
  l50 = 23
)


# (2) Define the context used to graph the results. Default values provided at instantiation time. However
# you can modify them as suits you best as PlotContext$new returns a R6 object
stack_plot_context <- chartlbi::PlotContext$new()

# (3) Define the threshold over which the LBI indicators will be evaluated. Default values provided at instantiation time.
thresholds <- chartlbi::Thresholds

# (5) Define indicator order you want them to be shown as
column_order <- list('Pmega', 'Lc_Lmat', 'L25_Lmat', 'Lmax5_Linf', 'Lmean_Lopt', 'Lmean_Lfem')

# (4) Run the LBI algorithm
lbi <- chartlbi::LbiAlgo$new(length_freq_matrix, params)
results <- lbi$run()

# (5) Plot the results
lbi_plotter <- chartlbi::OutputPlotter$new(results, stack_plot_context, thresholds)
graph <- lbi_plotter$build_plots(column_order)
graph
```
