---
title: "running-chartlbi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{running-chartlbi}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# 1. Installing `chartlbi` package
For this vigenette to work this package must be installed and exist in R's default libpath. The commented lines below need to be uncommented the first time you either run the whole document or this cell.

```{r setup}

# installed_packages <- rownames(installed.packages())
# if (!'chartlbi' %in% installed_packages) {
#   devtools::install_github("https://github.com/d2gex/chartlbi", dep=TRUE)
# }
# Ensure knitr does run the vignette from the same folder as interactively
knitr::opts_knit$set(root.dir = dirname(getwd()))
library("chartlbi")

```
# 2. Working Directory
This vigenette assumes that you are sitting on the root folder of your project. In otherwise situations please do use `setwd` as it suits you best.

# 3. Reading the sample data
 [Length-frequency](https://github.com/ices-tools-dev/LBI_shiny/blob/master/data/freqGad.csv) and [weight-at-length] (https://github.com/ices-tools-dev/LBI_shiny/blob/master/data/walGad.csv) matrices for gadoids in this example are provided by ICES.
```{r}
length_freq_matrix <- readRDS("vignettes/data/demersal_fish_sample.rds")


```
```{r}
head(length_freq_matrix)
```

```{r fig.width=8, fig.height=15}

# (1) Define biological inputs and size of class length
params <- AlgoParams$new()
params$binwidth <- 10
params$linf <- 49.1
params$l50 <- 23

# (2) Define the context used to graph the results. Default values provided at
# instantiation time.
stack_plot_context <- PlotContext$new()

# (3) Define the threshold over which the LBI indicators will be evaluated. Default values provided at instantiation time.
thresholds <- Thresholds$new()

# (5) Define indicator order you want them to be shown as
column_order <- list('Pmega','Lc_Lmat', 'L25_Lmat', 'Lmax5_Linf', 'Lmean_Lopt', 'Lmean_Lfem')

# (4) Run the LBI algorithm
lbi <- LbiAlgo$new(length_freq_matrix, params)
results <- lbi$run()

# (5) Plot the results
lbi_plotter <- OutputPlotter$new(results, stack_plot_context, thresholds)
graph <- lbi_plotter$build_plots(column_order)
graph
```
